### 2020-06-07 system-model.tex
:pencil: WIT initialization

			\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=\bar{\psi}_{n}

@@

					\State \textbf{Input} $\bar{R},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$
					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}

@@

					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$

@@

					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$

@@

				& \triangleq a^{(i)}\\

@@

				& \triangleq b^{(i)}

@@

					& \quad + \frac{1}{2}(a^{(i-1)} + b^{(i-1)})(a^{(i)} + b^{(i)}) - \frac{1}{4}(a^{(i-1)} + b^{(i-1)})^2 - \frac{1}{4}(a^{(i)} - b^{(i)})^2\label{eq:z_waveform_lb}\\
					g^{(i)}

@@

			Note that \ref{op:su_waveform_1} involves bilinear terms $\rho\mathrm{Tr}(\boldsymbol{A}_{I/P}\boldsymbol{W}_{I/P})$ and $(1-\rho)W_{I,n,n}$. We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$. Therefore, problem \ref{op:su_waveform_1} is equivalent to

@@

				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}

@@

@@

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ and $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$ for problem \ref{op:su_waveform}
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

			\psi_{I,n}^{\star}=\psi_{P,n}^{\star}=-\bar{\psi}_{n}

@@

					\State \textbf{Input} $\bar{R},Q,\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\boldsymbol{R}_n,\boldsymbol{C}_{I/P,n},\sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}\ \forall n$ by \ref{eq:t}

@@

					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$

@@

					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$

@@

				& \triangleq a^{(i)}\label{eq:a}\\

@@

				& \triangleq b^{(i)}\label{eq:b}

@@

					& \quad + \frac{1}{2}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})(\bar{a}^{(i)} + \bar{b}^{(i)}) - \frac{1}{4}(\bar{a}^{(i-1)} + \bar{b}^{(i-1)})^2 - \frac{1}{4}(\bar{a}^{(i)} - \bar{b}^{(i)})^2\label{eq:z_waveform_lb}\\
					g_n^{(i)}

@@

			Note that \ref{op:su_waveform_1} involves bilinear terms $\rho\mathrm{Tr}(\boldsymbol{A}_{I/P}\boldsymbol{W}_{I/P})$ and $(1-\rho)W_{I,n,n}$. We lower bound the objective function \ref{eq:su_waveform_target} and constraint \ref{eq:su_waveform_constraint_1} in \ref{eq:z_waveform_lb} and \ref{eq:r_power_lb} such that $\tilde{z}' \le \tilde{z}$ and $g_n(\rho,W_{I,n,n}) \le (1-\rho)W_{I,n,n}$. Therefore, problem \ref{op:su_waveform_1} is equivalent to

@@

				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho,\bar{a},\bar{b}}{\tilde{z}'(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{g_n(\rho,W_{I,n,n})\lvert h_n \rvert^2}{\sigma_n^2}\right)} \ge \bar{R}}

@@

				\addConstraint{a \ge \bar{a}}
				\addConstraint{b \ge \bar{b}}

@@

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,Q,\boldsymbol{R}_n,\sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $a^{(0)}$, $b^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and power splitting ratio $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\State Update auxiliary $a^{(i)},b^{(i)}$ by \ref{eq:a} and \ref{eq:b}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ and $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$ for problem \ref{op:su_waveform}
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}

		\begin{subsection}{WIT initialization}
			To characterize the R-E region, we initialize the algorithm to WIT mode and reduce the rate constraint gradually to obtain the boundary points. Consider a rate maximization problem with given information waveform $\boldsymbol{w}_I$ as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\sum_{n}{\log_2\left(1+\frac{\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}}{\label{op:su_irs_wit}}{}
				\addConstraint{\boldsymbol{\Phi}_{l,l}=1, \quad l=1,\dots,L+1}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1}
			\end{maxi!}
			Problem \ref{op:su_irs_wit} can be solved after SDR. Similar to section \ref{se:fs_irs}, a best solution $\bar{\boldsymbol{\phi}}^\star$ can be obtained via Gaussian randomization method and $\boldsymbol{\phi}^\star$ can be recovered by $\phi_l^\star=\phi_l^\star/\phi_{L+1}^\star, \ l=1,\dots,L$. After constructing composite channel by \ref{eq:h_k}, we use water-filling algorithm and matched filter to obtain optimal power allocation $p_n=\lvert w_{I,n} \rvert^2$ and waveform phase $\psi_{I,n}^\star=-\bar{\psi}_n$, respectively. Therefore, the optimal information waveform at subband $n$ is
			\begin{equation}\label{eq:w_wit}
				w_{I,n}=\sqrt{p_n}e^{j \psi_{I,n}^\star}
			\end{equation}
			We update IRS and information waveform iteratively by \ref{op:su_irs_wit} and \ref{eq:w_wit} until convergence. The WIT algorithm is summarized in \ref{alg:wit}.
			\begin{algorithm}
				\caption{WIT Initialization}
				\label{alg:wit}
				\begin{algorithmic}[1]
					\State \textbf{Input} $P, Q, \boldsymbol{R}_n, \sigma_n \ \forall n$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{w}_I^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Obtain IRS matrix $\boldsymbol{\Phi}^{(i)}$ by solving problem \ref{op:su_irs_wit}
					\State Perform EVD $\boldsymbol{\Phi}^{(i)}=\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}_{\boldsymbol{\Phi}^{(i)}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{(i)}}^{\frac{1}{2}}\boldsymbol{r}_q\right)}$ and matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$
					\State Select best solution $(\boldsymbol{\Phi}^{(i)})^\star$ and $(\boldsymbol{\phi}^{(i)})^\star$ for problem \ref{op:su_irs_wit}
					\State Update composite channel $\boldsymbol{h}^{(i)}$ by \ref{eq:h_k}
					\State Obtain optimal power allocation $p_n^{(i)} \ \forall n$ by water-filling algorithm
					\State Obtain optimal waveform phase $\psi_{I,n}^{(i)} \ \forall n$ by \ref{eq:psi}
					\State Update information waveform $\boldsymbol{w}_I^{(i)}$ by \ref{eq:w_wit}
					\Until $\lvert R^{(i)}-R^{(i-1)} \rvert \le \epsilon$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \boldsymbol{\phi}^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{subsection}
\end{section}
